\documentclass[10pt]{article}
\usepackage{paracol}
\usepackage[margin=0.9in]{geometry}
\usepackage{enumitem}
\usepackage[none]{hyphenat}

\renewcommand{\familydefault}{\sfdefault}
\setlist[itemize]{leftmargin=1.5em,itemsep=0em}
\begin{document}
\pagenumbering{gobble}

\section*{Matt Dalzell - {\large Staff Software Engineer and Technical Leader}}

\columnratio{0.30}
\setlength{\columnsep}{4em}
\setlength{\columnseprule}{0.1pt}
\begin{paracol}{2}

    % Contact Info
    \subsection*{Contact Info}
    contact@mattdalzell.com \\
    https://mattdalzell.com \\
    https://github.com/mdalzell

    % Technical Skills
    \subsection*{Technical Skills}

    % Frontend
    \textbf{Frontend}
    \begin{itemize}
        \item React
        \item Next.js
        \item TypeScript
        \item JavaScript/ES6+
        \item HTML5
        \item CSS
    \end{itemize}

    % Backend
    \noindent \textbf{Backend}
    \begin{itemize}
        \item NodeJS
        \item C\#/.NET
        \item Go
    \end{itemize}

    % Cloud Providers
    \noindent \textbf{Cloud Providers}
    \begin{itemize}
        \item AWS  \\ {\footnotesize{\textit{EC2 / S3 / CloudFront / \\ Certificate Manager}}}
        \item Azure \\ {\footnotesize{\textit{Event Hubs / Monitor}}}
    \end{itemize}

    % DevOps
    \noindent \textbf{DevOps}
    \begin{itemize}
        \item Terraform
        \item Docker
        \item LaunchDarkly
        \item Jenkins
    \end{itemize}

    % Education
    \subsection*{Education}
    \textbf{Georgia Insitute of Technology} \\
    Atlanta, GA (Remote) \\
    \textit{M.S. in Computer Science}  \\
    {\footnotesize{2022 - 2025}} \\


    \noindent \textbf{Northwestern University} \\
    Evanston, IL \\
    \textit{B.S. in Computer Science}  \\
    {\footnotesize{2009 - 2013}}

    % Other Honors
    \subsection*{Other Honors}
    \textbf{Eagle Scout} \\
    \textit{Boy Scouts of America} - {\footnotesize{2009}}

    \switchcolumn

    % Professional Experience
    \subsection*{Professional Experience}

    % Bread
    \textbf{Bread Financial} - Schaumburg, IL / New York, NY (Remote) \\
    \textit{Staff Software Engineer} - {\footnotesize{(June 2025 - Present)}}
    \begin{itemize}
        \item Coordinated frontend strategy for a greenfield B2B web application, working closely with product stakeholders, enterprise architects, and cybersecurity engineers to design a scalable and secure portal.
        \item Served as an interim engineering manager for a frontend team of 7 engineers for a period of 3 months.
    \end{itemize}
    \textit{Senior Software Engineer} - {\footnotesize{(October 2022 - June 2025)}}
    \begin{itemize}
        \item Lead React application development for a B2C lending product by defining the system's architecture, collaborating with the product team to write JIRA tickets, and guiding other engineers.
        \item Implemented a role-based access control (RBAC) system using Okta, feature flags, and tenant-based configuration.
        \item Audited mobile application code written by a third party contracting company and consolidated the findings into a presentation for the senior leadership team.
        \item Established a cross-team frontend guild to share knowledge among engineers across the organization.
        \item Improved Bread's engineer interview experience by creating new questions to assess a candidate's frontend coding and system design ability in a fair and unbiased manner.
    \end{itemize}
    \textit{Software Engineer II} - {\footnotesize{(November 2020 - October 2022)}}
    \begin{itemize}
        \item Collaborated with internal stakeholders in product, design, and customer service to extend the functionality of an internal loan servicing application.
        \item Won first place in Bread's "Shark Tank" competition by pitching a feature prototype to senior executive leadership.
    \end{itemize}

    % BMW Technology
    \noindent \textbf{BMW Technology Corporation} - Chicago, IL \\
    \textit{Software Engineer} - {\footnotesize{(July 2019 - October 2020)}} \\
    {\footnotesize{Contractor via Apex Systems}}
    \begin{itemize}
        \item Built C\#/.NET Core microservices as part of a distributed system to facilitate dealership payments using Azure Event Hubs for Kafka.
        \item Created a NodeJS composite service for the My BMW mobile application, orchestrating multiple microservices into a single appointment booking API for the client.
    \end{itemize}


    % Inspire11
    \noindent \textbf{Inspire11} - Chicago, IL \\
    \textit{Consultant (Frontend Engineer)} - {\footnotesize{(January 2019 - July 2019)}}
    \begin{itemize}
        \item Provided expertise in React for a fintech company as the primary frontend engineer of a remote agile team.
    \end{itemize}

    % VelocityEHS
    \noindent \textbf{VelocityEHS} - Chicago, IL \\
    \textit{Software Engineer II} - {\footnotesize{(November 2015 - December 2018)}}
    \begin{itemize}
        \item Designed, implemented, and deployed a React SaaS application as part of a multi-year rewrite of a core product.
        \item Rewrote the existing C\#/.NET data access layer, services, and APIs using the SOLID principles of object oriented programming.
    \end{itemize}

    % Azavar Technologies
    % \noindent \textbf{Azavar Technologies} - Chicago, IL \\
    % \textit{Web Developer} - {\footnotesize(June 2013 - November 2015)}
    % \begin{itemize}
    %    \item Built web applications for clients across a variety of industries using the .NET framework and Bootsrap for responsive frontend layouts.
    % \end{itemize}

\end{paracol}
\end{document}